% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Luis Rivera - Resume},
  pdfauthor={Luis Rivera},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Luis Rivera - Resume}
\author{Luis Rivera}
\date{2025-04-02}

\begin{document}
\maketitle


\section{Contact Information}\label{contact-information}

\begin{itemize}
\tightlist
\item
  \textbf{Phone:} 3039606369\\
\item
  \textbf{Email:} lrivera30ds@gmail.com\\
\item
  \textbf{LinkedIn:}
  \href{https://linkedin.com/in/luisrivera98}{linkedin.com/in/luisrivera98}
\end{itemize}

\section{Areas of Expertise}\label{areas-of-expertise}

\begin{itemize}
\tightlist
\item
  Algorithm tools\\
\item
  Design metrics\\
\item
  Object-oriented programming\\
\item
  Data spreadsheet summarization\\
\item
  Probability distributions\\
\item
  Hypothesis testing\\
\item
  R programming\\
\item
  Statistical testing\\
\item
  Data analysis/evaluation\\
\item
  Regression modeling\\
\item
  Research techniques\\
\item
  Research design\\
\item
  Process planning\\
\item
  Quality management\\
\item
  Forecasting tools\\
\item
  Policy analysis\\
\item
  SQL commands, joins\\
\item
  Database design\\
\item
  Data merging\\
\item
  HTML proficiency\\
\item
  CSS styling proficiency
\end{itemize}

\section{Education}\label{education}

\subsection{Bachelor of Arts in Public Policy and
Administration}\label{bachelor-of-arts-in-public-policy-and-administration}

\textbf{Brigham Young University - Idaho} \textbar{} Rexburg, ID\\
\textbf{Sep 2018 - Dec 2021}\\
- Emphasis in Public Administration\\
- \textbf{GPA:} 3.89\\
- Academic Scholarship - Thomas E. Ricks Grant

\subsection{Bachelor of Science in Data Science Online
Coursework}\label{bachelor-of-science-in-data-science-online-coursework}

\textbf{Brigham Young University - Idaho} \textbar{} Rexburg, ID\\
\textbf{Aug 2024 - Present}\\
- Additional courses taken through the BYU-I BS in Data Science major as
prerequisite coursework for MS in Data Science.

\section{Professional Experience}\label{professional-experience}

\subsection{Admin Analyst I}\label{admin-analyst-i}

\textbf{New Jersey Department of Transportation} \textbar{} Ewing, NJ\\
\textbf{Jan 2023 - May 2024}\\
- Developed internal protocols for managing \$3.5 million in annual
federal funds related to the Intelligent Transportation Resource Center.
- Managed federal contracts using the Financial Management Information
System. - Conducted research on Intelligent Transportation Systems to
improve traffic flow and safety. - Provided support in developing the
annual in-house budget for the Transportation Mobility Research Unit. -
Participated in State Transportation Innovation Council quarterly
meetings.

\subsection{Instructor Eval/Statistics
TA}\label{instructor-evalstatistics-ta}

\textbf{Brigham Young University-Idaho} \textbar{} Rexburg, ID\\
\textbf{Apr 2021 - Dec 2021}\\
- Assigned grades for student coursework. - Conducted exam review
sessions and tutoring for a class of 50 students. - Monitored BYU-I
online instructor presence for 24 instructors daily.

\subsection{Custodian}\label{custodian}

\textbf{Brigham Young University-Idaho} \textbar{} Rexburg, ID\\
\textbf{Jan 2019 - Apr 2020}\\
- Performed routine cleaning and maintenance tasks across campus
buildings. - Managed waste disposal and maintained cleanliness in waste
areas. - Assisted with event setups and post-event cleanups.

\subsection{Ambassador}\label{ambassador}

\textbf{Church of Jesus Christ of Latter-day Saints} \textbar{} San
Fernando, CA\\
\textbf{Aug 2016 - Jul 2018}\\
- Oversaw the well-being of 30 full-time ambassadors. - Provided
community service and humanitarian aid. - Shared the teachings of Jesus
Christ and engaged in religious education. - Trained ambassadors for
missionary life and responsibilities.




\end{document}
